Multiple quantum NMR in solids as a method of a determination of Wigner--Yanase skew information

### 2021-02-19 manuscript.tex
Add keywords and highlights

%%Research highlights
%\begin{highlights}
%\item Research highlight 1
%\item Research highlight 2
%\end{highlights}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
multiple quantum (MQ) NMR \sep
%% PACS codes here, in the form: \PACS code \sep code
%\PACS 0000 \sep 1111
%%
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC 0000 \sep 1111
\end{keyword}

>>>>

%%Research highlights
\begin{highlights}
	\item multiple quantum NMR spectroscopy
	\item connection of the Wigner-Yanase skew information and the second moment of the distribution of multiple quantum coherences
	\item the dependence of the number of entangled spins on temperature
\end{highlights}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
	many-spin entanglement \sep
	Fisher information \sep
	Wigner-Yanase skew information \sep
	multiple quantum NMR \sep
	multiple quantum coherences \sep
	second moment \sep
	temperature
%% PACS codes here, in the form: \PACS code \sep code
%\PACS 0000 \sep 1111
%%
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC 0000 \sep 1111
\end{keyword}
